The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-07-12 WavesData-2019/LatexNotes/notes.tex
NM

We will primarily consider the case in which waves originate from a region of constant depth, encounter an abrupt depth change, and then continue in another region of constant depth. Thus, depth will be piecewise constant
\begin{align}
\depth = 
\begin{cases}
\it \dup \quad \mbox{if } x<0 \\
\it \ddn \quad \mbox{if } x>0
\end{cases}
\end{align}
Most often, we will consider waves moving into shallower depth, so that $\ddn < \dup$. The incoming waves are randomized and generated with a peak forcing frequency of $\freqp$.

@@

\vsp{10}
Old notes:
The dimensionless KdV equation is
\begin{align}
\label{varKdV}
u_t + \ampp D^{-3/2} \, u u_x + \mu D^{1/2} \, u_{xxx} = 0
\end{align}
with the dimensionless parameters
\begin{align}
\label{ndKdV}
\ampp = \eps \delta^{-2} = \frac{ag}{h_0^2 f_p^2} , \qquad
\mu = \frac{4 \pi^2}{9 \lamfac^2}
\end{align}
Here, the displacement has been scaled on the characteristic wave amplitude, $u = \eta/a$, where $a = \etastd= \mean{\eta^2}^{1/2}$.
As a consequence, $u$ has fixed energy
\begin{equation}
E[u] = \frac{1}{2} \intt u^2 \dx = \frac{1}{2}
\end{equation}

>>>>

We will primarily consider the case in which waves originate from a region of constant depth, encounter an abrupt depth change, and then continue in another region of constant depth. Thus, depth will be piecewise constant
\begin{align}
\depth = 
\begin{cases}
\it \dup \quad \mbox{if } x<0 \\
\it \ddn \quad \mbox{if } x>0
\end{cases}
\end{align}
Most often, we will consider waves moving into shallower depth, so that $\dup > \ddn$. The incoming waves are randomized and generated with a peak forcing frequency of $\freqp$.

@@

\vsp{10}
Old notes here (I need to make sure everything is consistent and then remove this section below in favor of the newer, simpler writeup above).
The dimensionless KdV equation is
\begin{align}
\label{varKdV}
u_t + \ampp D^{-3/2} \, u u_x + \mu D^{1/2} \, u_{xxx} = 0
\end{align}
with the dimensionless parameters
\begin{align}
\label{ndKdV}
\ampp = \eps \delta^{-2} = \frac{ag}{h_0^2 f_p^2} , \qquad
\mu = \frac{4 \pi^2}{9 \lamfac^2}
\end{align}
Here, the displacement has been scaled on the characteristic wave amplitude, $u = \eta/a$, where $a = \etastd= \mean{\eta^2}^{1/2}$.
As a consequence, $u$ has fixed energy
\begin{equation}
E[u] = \frac{1}{2} \intt u^2 \dx = \frac{1}{2}
\end{equation}
